Associations_PFN_Cognition

### 2023-04-20 Step1_TotalCorticalRepresentation/Associations_PFN_Cognition.Rmd
added comments

cbcl<-read.table("/Users/askeller/Documents/Kellernet_PrelimAnalysis/aseba/abcd_cbcls01.txt",header=TRUE)
cbcl_baseline <- cbcl[cbcl$eventname=="baseline_year_1_arm_1",c("subjectkey","cbcl_scr_syn_internal_r","cbcl_scr_syn_external_r","cbcl_scr_syn_totprob_r")]
cbcl_baseline$cbcl_scr_syn_internal_r <- as.numeric(cbcl_baseline$cbcl_scr_syn_internal_r)
cbcl_baseline$cbcl_scr_syn_external_r <- as.numeric(cbcl_baseline$cbcl_scr_syn_external_r)
cbcl_baseline$cbcl_scr_syn_totprob_r <- as.numeric(cbcl_baseline$cbcl_scr_syn_totprob_r)

psychMed<-read.csv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/PsychotropicMeds/ABCD_Psychotropic_Medications.csv")
psychMed_baseline <- psychMed[psychMed$eventname=="baseline_year_1_arm_1",c("subjectkey","ADHD_meds","Antidepressant_meds","Antipsychotic_meds")]
psychMed_baseline$ADHD_meds<-as.factor(psychMed_baseline$ADHD_meds)
psychMed_baseline$Antipsychotic_meds<-as.factor(psychMed_baseline$Antipsychotic_meds)
psychMed_baseline$Antidepressant_meds<-as.factor(psychMed_baseline$Antidepressant_meds)

abcd.data.traintest<-merge(abcd.data.traintest,cbcl_baseline,by="subjectkey")
abcd.data.traintest<-merge(abcd.data.traintest,psychMed_baseline,by="subjectkey")

abcd.data.traintest$ADHD_meds<-factor(abcd.data.traintest$ADHD_meds, levels = c("1","0"))
abcd.data.traintest$Antidepressant_meds<-factor(abcd.data.traintest$Antidepressant_meds, levels = c("1","0"))
abcd.data.traintest$Antipsychotic_meds<-factor(abcd.data.traintest$Antipsychotic_meds, levels = c("1","0"))

@@

# Test whether results hold with covariates for psychotropic med use:
```{r}
abcd.data.train.harmonized.withMeds <- merge(abcd.data.train.harmonized,abcd.data.traintest[,c("subjectkey", setdiff(colnames(abcd.data.traintest),colnames(abcd.data.train.harmonized)))],by="subjectkey")
abcd.data.test.harmonized.withMeds <- merge(abcd.data.test.harmonized,abcd.data.traintest[,c("subjectkey", setdiff(colnames(abcd.data.traintest),colnames(abcd.data.test.harmonized)))],by="subjectkey")

>>>>

# load in CBCL data for internalizing, externalizing, and problem behavior symptoms
cbcl<-read.table("/Users/askeller/Documents/Kellernet_PrelimAnalysis/aseba/abcd_cbcls01.txt",header=TRUE)
cbcl_baseline <- cbcl[cbcl$eventname=="baseline_year_1_arm_1",c("subjectkey","cbcl_scr_syn_internal_r","cbcl_scr_syn_external_r","cbcl_scr_syn_totprob_r")]
cbcl_baseline$cbcl_scr_syn_internal_r <- as.numeric(cbcl_baseline$cbcl_scr_syn_internal_r)
cbcl_baseline$cbcl_scr_syn_external_r <- as.numeric(cbcl_baseline$cbcl_scr_syn_external_r)
cbcl_baseline$cbcl_scr_syn_totprob_r <- as.numeric(cbcl_baseline$cbcl_scr_syn_totprob_r)

# load in psychotropic medication data (assessed by the Medication Inventory from the PhenX instrument and coded according to Shoval et al., 2021)
psychMed<-read.csv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/PsychotropicMeds/ABCD_Psychotropic_Medications.csv")
psychMed_baseline <- psychMed[psychMed$eventname=="baseline_year_1_arm_1",c("subjectkey","ADHD_meds","Antidepressant_meds","Antipsychotic_meds")]
psychMed_baseline$ADHD_meds<-as.factor(psychMed_baseline$ADHD_meds)
psychMed_baseline$Antipsychotic_meds<-as.factor(psychMed_baseline$Antipsychotic_meds)
psychMed_baseline$Antidepressant_meds<-as.factor(psychMed_baseline$Antidepressant_meds)

# merge dataframes
abcd.data.traintest<-merge(abcd.data.traintest,cbcl_baseline,by="subjectkey")
abcd.data.traintest<-merge(abcd.data.traintest,psychMed_baseline,by="subjectkey")

# code medication use as a factor
abcd.data.traintest$ADHD_meds<-factor(abcd.data.traintest$ADHD_meds, levels = c("1","0"))
abcd.data.traintest$Antidepressant_meds<-factor(abcd.data.traintest$Antidepressant_meds, levels = c("1","0"))
abcd.data.traintest$Antipsychotic_meds<-factor(abcd.data.traintest$Antipsychotic_meds, levels = c("1","0"))

@@

# Test whether results hold with covariates for psychotropic med use:
```{r}
# merge data frames
abcd.data.train.harmonized.withMeds <- merge(abcd.data.train.harmonized,abcd.data.traintest[,c("subjectkey", setdiff(colnames(abcd.data.traintest),colnames(abcd.data.train.harmonized)))],by="subjectkey")
abcd.data.test.harmonized.withMeds <- merge(abcd.data.test.harmonized,abcd.data.traintest[,c("subjectkey", setdiff(colnames(abcd.data.traintest),colnames(abcd.data.test.harmonized)))],by="subjectkey")
